Reasonably Programmable Literal Notation

### 2018-06-25 icfp18/syntax-icfp18.tex
added brief mention of debugging paper and active code completion paper

At several points, we allude to editor integration. However, several important questions having to do with TLM-specific syntax highlighting, incremental parsing and error recovery \cite{graham1979practical} remain to be considered. Another interesting direction would be to generalize TLMs to support non-textual notation in the setting of a structure editor \cite{DBLP:conf/popl/OmarVHAH17,snapl17}.

@@

\paragraph{Concluding Remarks} 
To conclude, let us briefly reiterate the key ideas of this paper. The focus was on ensuring that client programmers can follow simple protocols when they have questions about the syntactic structure, type structure or binding structure of a program. In answering these sorts of questions,  the client is not made to look at the generated expansion itself, nor inspect the parser implementation. Instead, the programmer need only be given knowledge of the expansion type from the TLM definition and the segmentation inferred by the expander at each application site, which carries a small volume of information that can be communicated straightforwardly by standard editor services. Certain questions related to the binding structure simply do not need to be asked due to the strict context independence and capture avoidance discipline of the system, enabled by the explicit tracking of dependencies and of spliced segments.

>>>>

At several points, we allude to editor integration. However, several important questions having to do with TLM-specific syntax highlighting, incremental parsing and error recovery \cite{graham1979practical}, as well as debugging \cite{DBLP:journals/scp/CulpepperF10}, remain to be considered. Another interesting direction would be to generalize TLMs to support non-textual notation in a structure editor \cite{DBLP:conf/popl/OmarVHAH17,snapl17}, thereby internalizing active code completion \cite{Omar:2012:ACC:2337223.2337324}.

@@

\paragraph{Concluding Remarks} 
To conclude, let us briefly reiterate the key ideas of this paper. The focus was on ensuring that client programmers can follow simple protocols when they have questions about the syntactic structure, type structure or binding structure of a program. In answering these sorts of questions,  the client is not made to look at the generated expansion itself, nor inspect the parser implementation. Instead, the programmer need only be given knowledge of the expansion type from the TLM definition and the segmentation inferred by the expander at each application site, which carries a small volume of information that can be communicated straightforwardly by standard editor services. Certain questions related to the binding structure simply do not need to be asked due to the strict context independence and capture avoidance discipline of the system.%enabled by the explicit tracking of dependencies and of spliced segments.
